---
title: "NSW COVID-19 Cases by Age Group"
author: "Jiaxin Lu"
date: 2021-11-11T21:13:14-05:00
categories: ["R"]
tags: ["NSW", "COVID-19", "Age"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

# NSW COVID-19 Cases By Age Group

```{r import, include=FALSE}
library(dplyr)
library(tidyverse)
library(plotly)
library(ggplot2)
library(scales)
library(RColorBrewer)
library(gridExtra)
library(ggthemes)
library(highcharter)
library(DT)
library(leaflet)

setwd("C:/Users/32631/Documents/Rstudio/R_A3")
age <- read.csv("confirmed_cases_table2_age_group.csv")

```

The bar chart below shows the NSW COVID-19 cases by age group.

This bar chart claims that the most COVID-19 patients are concentrated in adolescents aged 0-19 in NSW. 

It may emphasise that teenagers prefer to play or study together. They may not willing to follow their parent's teachings, and they don’t like staying at home. 

As a result, they may become the main contagious. However, they have had better resistance due to a healthy body.

```{r age group, echo=FALSE}
age%>%
  group_by(age_group)%>%
  summarise(COVID_19_Cases = (count=n()))%>%
  ggplot()+
  geom_col(mapping = aes(y = age_group, x = COVID_19_Cases), fill = hue_pal()(4)[1], width = 0.6)+
  ggtitle("COVID-19 Cases by Age Group") +
  scale_fill_brewer(palette = "Blues")+
  theme(plot.title = element_text(hjust = 0.5, face = 'bold'))
```

Tips! If you are a resident of NSW, please monitor your children at some special time, they may cause serious consequences.
